---
title: "Tutorial 3"
author: "Pradip Basnet"
---

task 1: installing the necesary packages for data manipulation and visualization

```{r}
library(ggplot2)
```

```{r}
#install.packages("skimr")
```
```{r}
library(skimr)
```

```{r}
#install.packages("dplyr")
```
```{r}
library(dplyr)
```
task 2: viewing the dataset
```{r}
library(ggplot2)

# Load the diamonds dataset
data(diamonds)

```

task 3: viewing the first six rows of the datasets
```{r}
head(diamonds)
```
task 4: viewing the last six rows of the datset
```{r}
tail(diamonds)
```
task 5: check the structure of the dataset
```{r}
str(diamonds)
```
task 6: check the dimension of the datset
```{r}
dim(diamonds)
```
task 7: summarize the data
```{r}
summary(diamonds)
```
task 8: install the library psych
```{r}
#install.packages("psych")

library(psych)
describe(diamonds)
```
task 9: obtaining the concise overview of the data set by displaying the structure and a preview of its contents.
```{r}
glimpse(diamonds)
```
task 10: summary of the counts for each unique value in the "cut" column of the diamonds
```{r}
diamonds %>%
  count(cut)
```
task 11: generates a frequency table of the "cut" variable in the diamonds dataset.
```{r}
table(diamonds$cut)
```
task 12:obtain both the frequency information and the distinct values of the dataset
```{r}
unique(diamonds$cut)
```
##Visualization

#Categorical variables
task 1: visual representation of the distribution of diamond cuts in the dataset(bar chart looking at diamond cut)
```{r}
ggplot(diamonds) + geom_bar(aes(x = cut))
```
##Continous Variable
task 2:a histogram plot that displays the distribution of the "carat" variable in the diamonds data set
```{r}
ggplot(diamonds) +
  geom_histogram(aes(x = carat), binwidth = 0.5)
```
##Data Cleaning
task 1: filter data set to create new data set that contain all the information from the original data set, but only for diamonds with a carat value less than 3
```{r}
small <- diamonds %>% filter(carat < 3)
```

task 2: visual representation of the distribution of carat values for smaller diamonds in data set, allowing you to observe count of diamonds within each bin.
```{r}
ggplot(small) +
  geom_histogram(aes(x = carat), binwidth = 0.1)
```
##Covariation

#Categorical vs Continous
task 1:create a frequency polygon plot that displays the distribution of diamond prices in the diamonds data set
```{r}
ggplot(diamonds, aes(x=price)) +
  geom_freqpoly(aes(color=cut), binwidth = 500, linewidth=1.5)
```
task 2:create a box plot that visualizes the distribution of diamond prices across different categories of the "cut" variable
```{r}
ggplot(diamonds, aes(x=cut, y=price)) + geom_boxplot()
```
task 3 :grouping and counting on the "color" and "cut" variables in the data set and creates a tile plot to visualize the counts of combinations
```{r}
diamonds %>% count(color, cut) %>% ggplot(aes(x=color, y=cut)) + geom_tile(aes(fill=n))
```
##Continous vs Continous
task 1:creates a scatter plot that displays the relationship between the carat and price variables of diamonds in the diamonds data set
```{r}
ggplot(diamonds, aes(x=carat, y=price)) + geom_point(alpha=1/100)
```
task 2:create hexbin plot that visualizes the density of data points based on the "carat" and "price" variables in data set.
```{r}
ggplot(diamonds)+geom_hex(aes(x=carat, y=price))
```
task 3:create a dodged bar plot that displays the distribution of diamonds based on their "cut" and "clarity" attributes
```{r}
ggplot(diamonds,aes(x=cut,fill=clarity)) + geom_bar(position = "dodge")
```

```{r}
#calculate the distribution of the transmisson
trans_dist <- table(diamonds$cut)

# Create pie chart
pie(trans_dist, 
    labels = c("Fair", "Good", "Very Good", "Premium", "Ideal"), 
    main = "Quality of cut")
```
#clustering
task 1: loading the necessary packages
```{r}
library(ggplot2)
#install.packages("factoextra")
library(factoextra)
```
task 2: set a random seed
```{r}
set.seed(7696)
```


task 3: viewing the dataset 
```{r}
data("diamonds")
#View(diamonds)
```

task 4: filter data by column name
```{r}
data1 =  diamonds[,c("price", "carat")]
```

task 5: draw a scatter plot
```{r}
ggplot(diamonds, aes(x=price, y=carat))+geom_point()
```
task 6: cluster
```{r}
clusters = kmeans(data1,5)
clusters
```
task 8:
```{r}
cluster_index = as.factor(clusters$cluster)
ggplot(data1, aes(x=price, y=carat, color=cluster_index)) +geom_point()
```
task 9: filter data by column name
```{r}
data2 = diamonds[,c("price", "carat","table")]

```

task 10: 
```{r}
ggplot(diamonds, aes(x = price, y = carat, color = table)) + geom_point()
```
task 11: clustering
```{r}
clusters1 = kmeans(data2, 5)
clusters1
```
task 12:
```{r}
  fviz_cluster(clusters1, data = data2, geom = c("point"))
```

```{r}
clusters3 = kmeans(data2, 5, nstart=25)
clusters3
fviz_cluster(clusters3, data=data2, geom=c("point"))
```




 